Algebraic File Synchronization: Adequacy and Completeness

### 2016-10-11 p2/def-commands.tex
Introduction of partial functions

\begin{mydef}[Regular commands]
Therefore we have three pieces of information related to each command,
and represent them using triples that contain
their input type ($[v_\textrm{in}]$), output value ($v_\textrm{out}$),
and the node to which they are applied ($n$):
\[ \caaaa{v_\textrm{in}}{v_\textrm{out}}{n}. \]
\end{mydef}

>>>>

\begin{mydef}[Filesystem commands]
We model filesystem commands as partial endofunctions on filesystems,
that is, functions that map filesystems to filesystems, but which
are not defined everywhere.
%% TODO Return \bottom where undefined.

TODO. Therefore we have three pieces of information related to each command,
and represent them using triples that contain
their input type ($[v_\textrm{in}]$), output value ($v_\textrm{out}$),
and the node to which they are applied ($n$):
\[ \caaaa{v_\textrm{in}}{v_\textrm{out}}{n}. \]
\end{mydef}
